A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-08 paper.tex
First comments
In Spanish for now :)

There can be different types. Type-2 \cite{mendel2002type}, interval
t2 \cite{liang2000interval} and \cite{mendel2006interval}

Type-2 is time-consuming. Shadowed sets \cite{pedrycz1998shadowed}

@@

\section{Related Work}

@@

intuitionistic inference engine \cite{cornelis2001compositional}

implementation of a ifis, castillo \cite{castillo2007intuitionistic}

@@

centroid of a type-2 fuzzy-set \cite{karnik2001centroid}

@@

\section{Proposed Method}

The method, for now, consists on the procedures and elements
necessary to construct a basic Intuitionistic Fuzzy Inference System
(IFIS). This design was completed in order to make comparisons against
classic Fuzzy Inference Systems (FISs), such as Type-1 FIS, Interval
Type-2 and General Type-2 FIS, and prove that
the design was viable and able to contribute to better results than
the classic FISs.

In many works, intuitionistic fuzzy sets (IFSs) are constructed by
hand, by interviewing experts who assign memberships and
non-memberships to each of the values of a set (such as in
\cite{davarzani2013novel}). This work proposes a convenient way of
creating an IFS, imitating many systems that use Gaussian
membership functions (MFs) to facilitate an expert the representation of a
fuzzy interpretation. An example of an IFS is depicted in
Fig. \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
the MF as the red line, and the non-membership
function (NMF) as the blue line. In order to contruct the NMF, one has
to rotate a normal Gaussian MF by 180˚, and this can be seen as the
complement of the fuzzy set corresponding to a Gaussian MF.

@@

Two convenient ways of modifying the NMF and
satisfy (\ref{intuitionistic-interval}) are as follows: 1) one can set
the mean and the standard deviation of the Gaussian functions to be
the same, and only vary the $height$ of the NMF,
as is depicted in Fig. \ref{ifs}; and 2) one can set different means and
standard deviations of the Gaussian membership and non-membership
functions, but the $height$ of the MF must be equal
to $h_{mf} = 1 - h_{nmf}$, as this ensures that
(\ref{intuitionistic-interval}) is satisfied. An example of the latter
case is shown in Fig. \ref{ifs-diff-mu-sd}. To clarify, the $height$
of the MF ($h_{mf}$) of an IFS is equal to $max(\mu(x))$, and the
$height$ of the NMF ($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.

@@

The first step in an inference process in a classic FIS (a flow chart
for the process in an IFIS is given in Fig. \ref{flow-chart}) is to
determine what membership corresponds to a given input, given a set of
MFs. This is straightforward in a classic FIS, as the
membership to each input is already established in the membership
fuzzy set. For an IFIS, this work proposes a method to determine a
membership given a MF and a NMF,
which is described in (\ref{imembership}), and receives the name of
$i\mu$ (intuitionistic membership).

@@

The next step in the inference process is to perform an $\alpha$-cut
on the associated consequents to the antecedents that are activated by
the inputs. In a classic FIS, this process is straightforward, as the
memeberships in a fuzzy set representing a consequent are ``cut'' by
following (\ref{alpha-cut}) for every element in a fuzzy set
representing a consequent. In an intuitionistic MF, one can follow
the same procedure in order to obtain the $\alpha$-cut in the MF part,
but to obtain the $\alpha$-cut in the NMF, (\ref{nmf-alpha-cut}) must
be followed. In (\ref{nmf-alpha-cut}), the counterintuitive part is
that one has to find the corresponding $\nu$ for a given
$\mu_{\alpha}$. An example of an $\alpha$-cut, with $\mu_{\alpha} =
0.6$, is depicted in Fig. \ref{alpha-cut-example}.

@@

Finally, one has to defuzzify the aggregation of the $\alpha$-cut
consequents, in order to obtain a crisp number that represents
it. There are a number of methods that can be used to defuzzify a
fuzzy set, but the most frequently found in the literature is the
Center of Area (CoA), or simply centroid. One can obtain the centroid
of a classic fuzzy set A by using (\ref{center-of-area}). For an
IFS, one can use the concept of intuitionistic membership ($i\mu$) and
extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).

@@

The initial (and ambitious) hypothesis is that a Type-1 Intuitionistic Fuzzy System (T1-IFIS)
should perform better than a T1-FIS, as it can handle both uncertainty
and indeterminacy, and it is unclear if an IFIS should perform better
than a T2-FIS. The experiments presented in this work
cannot prove this statement profoundly, as the results will only test for a
single situation, which is the prediction of a subset of the
Mackey-Glass time series.

@@

Results can be found on https://github.com/amherag/wcci-2016-a

>>>>

%Empieza aquí 
There can be different types. Type-2 \cite{mendel2002type}, interval
t2 \cite{liang2000interval} and \cite{mendel2006interval}

%o incluso aquí
Type-2 is time-consuming. Shadowed sets \cite{pedrycz1998shadowed}

@@

% (Mario): 
% Más que definir los elementos, mejor justificar el motivo de la propuesta
% al parecer es por que Type-2 is time-consuming  
% Esto si:
% What is a intuitionistic fuzzy set 
% Y después justificar, debido a esto, proponemos un FIS intucionista
% Después lo clasico de como esta dividido el trabajo
\section{Related Work}

@@

intuitionistic inference engine \cite{cornelis2001compositional} %Que diferencias hay?

implementation of a ifis, castillo \cite{castillo2007intuitionistic} %Por?

@@

centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?

@@

\section{Proposed Method}
%(Mario)Is a Method? Extension? Implementation?
The method, for now, consists on the procedures and elements
necessary to construct a basic Intuitionistic Fuzzy Inference System
(IFIS). %(Mario)Por que basic?
%(Mario)Tal vez enumerarlas? cuales procedures son?
This design was completed in order to make comparisons against
classic Fuzzy Inference Systems (FISs), such as Type-1 FIS, Interval
Type-2 and General Type-2 FIS, and prove that
the design was viable and able to contribute to better results than
the classic FISs.
%(Mario)Es el proposito del diseño comparar? Creo que puedes decir mejor algo como:
%In order to assess the advantage of our proposal in terms of X
%a comparassion with  Type-1 FIS, Interval Type-2 and General Type-2 FIS,
%is presented.
%que se vea que tiene su merito propio, y lo comparamos para
%evaluar y comprobar su viabilidad
%Lo de Design me ocasiona ruido, parece que fuera una implementación
%Si no lo es, tal vez se puede decir algo como:
%The proposed method was implemented in order to make.

In many works, intuitionistic fuzzy sets (IFSs) are constructed manualy,
by interviewing experts who assign memberships and
non-memberships to each of the values of a set (such as in %to each of the members of a set?
\cite{davarzani2013novel}). This work proposes a convenient way of
creating an IFS, imitating many systems that use Gaussian
membership functions (MFs) to facilitate an expert the representation of a
fuzzy interpretation. An example of an IFS is depicted in
Fig. \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
the MF as the red line, and the non-membership
function (NMF) as the blue line. In order to contruct the NMF, one has
to rotate a normal Gaussian MF by 180˚, and this can be seen as the
complement of the fuzzy set corresponding to a Gaussian MF.
%(Mario)Al parecer lo que se está presentando es una manera automatizada de 
% hacer IFSs? Si  es así, es más facil presentarlo

@@

Two convenient ways of modifying a NMF and also
satisfying (\ref{intuitionistic-interval}) are the following: 1) setting
the mean and the standard deviation of the Gaussian functions to be
the same, and only vary the $height$ of the NMF,
as is depicted in Fig. \ref{ifs}; and 2) setting different means and
standard deviations of the Gaussian membership and non-membership
functions, while keeping the $height$ of the MF equal
to $h_{mf} = 1 - h_{nmf}$, as this ensures that
(\ref{intuitionistic-interval}) is satisfied. An example of the latter
case is shown in Fig. \ref{ifs-diff-mu-sd}. To clarify, the $height$
of the MF ($h_{mf}$) of an IFS is equal to $max(\mu(x))$, and the
$height$ of the NMF ($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.

@@

The first step of the inference process in a classic FIS (a flow chart
for the process in an IFIS is given in Fig. \ref{flow-chart}) is to
determine what membership corresponds to a given input, given a set of
%(Mario)determine what particular membership function corresponds to a 
% given input, given a set of 
MFs. This is straightforward in a classic FIS, as the
membership to each input is already established in the membership
fuzzy set. For an IFIS, this work proposes a method to determine a
membership given a MF and a NMF,
which is described in (\ref{imembership}), and receives the name of
$i\mu$ (intuitionistic membership). %(Mario)Creo que este podría ser el titulo

@@

The next step in the inference process is to perform an $\alpha$-cut % (Mario) La del FIS? aclaralo
on the associated consequents to the antecedents that are activated by
the inputs. In a classic FIS, this process is straightforward, as the
memeberships in a fuzzy set representing a consequent are ``cut'' by
following (\ref{alpha-cut}) for every element in a fuzzy set
representing a consequent. In an intuitionistic MF, one can follow
the same procedure in order to obtain the $\alpha$-cut in the MF part,
but to obtain the $\alpha$-cut in the NMF, (\ref{nmf-alpha-cut}) must
be followed. In (\ref{nmf-alpha-cut}), the counterintuitive part is
that one has to find the corresponding $\nu$ for a given
$\mu_{\alpha}$. An example of an $\alpha$-cut, with $\mu_{\alpha} =
0.6$, is depicted in Fig. \ref{alpha-cut-example}.

@@

Finally, one has to defuzzify the aggregation of the $\alpha$-cut 
consequents, in order to obtain a crisp number that represents
it. There are a number of methods that can be used to defuzzify a %Aclara que en los tipo Mamdani
fuzzy set, but the most frequently found in the literature is the
Center of Area (CoA), or simply centroid. One can obtain the centroid
of a classic fuzzy set A by using (\ref{center-of-area}). For an
IFS, one can use the concept of intuitionistic membership ($i\mu$) and
extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).

@@

The initial (and ambitious) hypothesis is that a Type-1 Intuitionistic Fuzzy System (T1-IFIS)
should perform better than a T1-FIS, as it can handle both uncertainty
and indeterminacy, and it is unclear if an IFIS should perform better
than a T2-FIS. The experiments presented in this work
cannot prove this statement profoundly, as the results will only be tested for a
single situation, which is the prediction of a subset of the
Mackey-Glass time series.

@@

The results of the experiment along with the code can be found on the 
following public Github repository: https://github.com/amherag/wcci-2016-a
